Globally-centered autocovariances in MCMC

### 2020-07-25 Paper/main.tex
Writing points down in blue.

The proof of the following theorem is available in Appendix~\ref{appendix:bias}.
\begin{theorem} \label{th:G-_expec} Under stationarity,
\[
   \mathbb{E} \left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
\]
and consequently,
\[
\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,. 
\]
   % \[
   % \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
   % \]
\end{theorem}

@@

\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]
\end{corollary}

@@

{\color{blue}Dootika: this section here needs to be much tighter in its presentation. We will need to remember that the paper is no longer about the SV estimators but about autocorrelations. So will have to present the discussion similarly. }

@@

@@

We are interested in the finding the bias for G-SVE estimator as a function of $n$. The proof below applies to all the important range of lag windows $w(x)$; where $w(x)$ is a continuous, even fnction with $w(0)=1, \abs{w(x)} < c$, and $\int_{-\infty}^{\infty}w^2(x)dx < \infty$. Define
%
\[
W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
\]

@@

\begin{theorem}\label{th:G-SVE_bias}
The limiting bias of replicated spectral variance is given by:
\[
 \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}
 \]
\end{theorem}

@@

\begin{ass} \label{ass:variance_cal}
Let $\{X_{st}\}_{t \geq 1}$ be the $s^{th}$ Markov chain for which SIP holds. 
\begin{enumerate}[a.]
    \item $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP
    \item $\E[X^4] < \infty$ where $\{X\}$ is the stochastic process
\end{enumerate}
\end{ass}

@@

\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown). Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor. Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$. The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$. Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed. The probability model is then,
%
\begin{align*}
    z_{ij} \mid x_1, ..., x_6 &\ sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
    y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
\end{align*}
%
\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$. We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$. $y_{ij}$ is specified only if $w_{ij} = 1$. The likelihood function is then,
%
\begin{multline*}
    L(x_1, x_2, x_3, x_4) \propto \\
\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]    
\end{multline*}

>>>>

The proof of the following theorem is available in Appendix~\ref{appendix:bias}.

{\color{blue} Fix the proof for this.}
\begin{theorem} \label{th:G-_expec} Under stationarity,
\[
   \mathbb{E} \left[\hat{\Gamma}_{G,s}(k) \right] = \left(1- \dfrac{|k|}{n}\right) \left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + o \left(n^{-2} \right)\,,
\]
and consequently,
\[
\mathbb{E} \left[\hat{\Gamma}_{G,s}(k) - \hat{\Gamma}(k)_s \right] = \dfrac{\abs{k}}{n}\left(1 - \dfrac{1}{m}\right)\left(\dfrac{\Sigma}{n} + \dfrac{\Phi}{n^2}\right) + o\left(n^{-2} \right)\,. 
\]
   % \[
   % \mathbb{E} \left[\hat{\Gamma}_{G}(k) \right] = \left(1- \dfrac{|k|}{n}\right)\left(\Gamma(k) - \dfrac{\Sigma}{mn} - \dfrac{\Phi}{mn^2}\right)  + \dfrac{2(m-1)}{m}\dfrac{\abs{k}}{n^2} \left(\Sigma - \sum_{h=0}^{n-1}\Gamma(h)\right) + o(n^{-2})
   % \]
\end{theorem}

@@

\begin{corollary} \label{cor:lag0_expectation}
\[
\mathbb{E} \left[\hat{\Gamma}_{G}(0) \right] = \Gamma(0) + \dfrac{\Sigma}{mn} + \dfrac{\Phi}{mn^2} + o(n^{-2})
\]

\end{corollary}

@@

@@

{\color{blue} Don't make this an assumption. Say this explicitly in Theorem 2. }

@@

{\color{blue}: Make the following an assumption. Is $2\pi$ needed? Is $W_n$ always finite? }
We are interested in the finding the bias for G-SVE estimator as a function of $n$. The proof below applies to all the important range of lag windows $w(x)$; where $w(x)$ is a continuous, even fnction with $w(0)=1, \abs{w(x)} < c$, and $\int_{-\infty}^{\infty}w^2(x)dx < \infty$. Define
%
\[
W_n = \dfrac{1}{2\pi}\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right).
\]

@@

{\color{blue} Under what assumptions?}
\begin{theorem}\label{th:G-SVE_bias}
The limiting bias of replicated spectral variance is given by:
\[
 \lim_{n \to \infty}b_n^q\mathbb{E} \left[\hat{\Sigma}_{G} - \Sigma \right] = -k_q\Phi^{(q)}
 \]
\end{theorem}

@@

{\color{blue} Don't make this a separate assumption. Include in the statement of the theorem}
\begin{ass} \label{ass:variance_cal}
Let $\{X_{st}\}_{t \geq 1}$ be the $s^{th}$ Markov chain for which SIP holds. 
\begin{enumerate}[a.]
    \item $\E[D^4] < \infty$ where D is a finite random variable associated with the SIP
    \item $\E[X^4] < \infty$ where $\{X\}$ is the stochastic process
\end{enumerate}
\end{ass}

@@

\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown). Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor. Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$. The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$. Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed. The probability model is then,
%
\begin{align*}
    z_{ij} \mid x_1, ..., x_6 & \sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
    y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
\end{align*}
%
\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$. We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$. $y_{ij}$ is specified only if $w_{ij} = 1$. The likelihood function is then,
%
\begin{multline*}
    L(x_1, x_2, x_3, x_4) \propto \\
\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]    
\end{multline*}
